The Decline of US Birth Rates: Analyzing Minimum Wages, Abortion Policies, Education, and Child Support Enforcement

### 2024-02-15 paper/paper.qmd
adjusted title

---
title: "Red States = Red Flags?"
subtitle: "An analysis of birth rate trends from 2001 to 2019 and an exploration of political affiliation of different states and Birth rates in the United States,"
author: 
  - Rayan Awad Alim
  - Maria Mangru
  - Isha Junega
thanks: "Code and data are available at: https://github.com/RayanAlim/Birth_Rate_Analysis"
date: today
date-format: long
abstract: "Melissa S. Kearney, Phillip B. Levine, and Luke Pardue in their paper, 
'The Puzzle of Falling US Birth Rates since the Great Recession', analyze the 
decreasing birth rates within the US. In this paper, we repicate use their data 
and replicate their results of their study. While they focused on examining 
birth rates by demographics, we focus on minimum wages, education, abortion 
poilicy, and child support enforcement. The importance of our research is that 
it highlights the underlying cause of why parents may not to have many children, 
which leads to a decline in birthrates."
format: pdf
number-sections: true
#bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "The Decline of US Birth Rates: Analyzing Minimum Wages, Abortion Policies, Education, and Child Support Enforcement"
subtitle:  "Reproduction of ‘The Puzzle of Falling US Birth Rates since the Great Recession’ (Kearney, Levine and, Pardue,2022)"

author: 
  - Rayan Awad Alim
  - Maria Mangru
  - Isha Junega
thanks: "Code and data are available at: https://github.com/RayanAlim/Birth_Rate_Analysis"
date: today
date-format: long
abstract: "Melissa S. Kearney, Phillip B. Levine, and Luke Pardue in their paper, 
'The Puzzle of Falling US Birth Rates since the Great Recession', analyze the 
decreasing birth rates within the US. In this paper, we repicate use their data 
and replicate their results of their study. While they focused on examining 
birth rates by demographics, we focus on minimum wages, education, abortion 
poilicy, and child support enforcement. The importance of our research is that 
it highlights the underlying cause of why parents may not to have many children, 
which leads to a decline in birthrates."
format: pdf
number-sections: true
#bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---
